---
title: "supermarket sales"
author: "Mingwei Wu"
output: pdf_document
---
# Data Description
## Id: computer generated sales slip invoice indentification number
## Branch: branch of supercenter (3 branches are avaliable identified by A, B and C)
## City: Location of supercenters
## Type: type of customers, recorded by members for customers using member card and normal for without member card
## Gender: gender type of customer
## Product: general item categorization groups - electronic accessories, fashion accessories, food and beverages, health and beauty, home and lifestyle, sports and travel
## Price: price of each product in dollar
## Quantity: numbers of products purchased by customer
## Tax: 5% tax fee for customer buying
## Total: total price including tax
## Date: date for purchase (record available from Jan 2019 to March 2019)
## Time: purchase time (10am to 8pm)
## Payment: payment used by customer for purchase(3 methods are available - Cash, Credit card and Ewallet)
## COGS: cost of goods sold
## Gross income: gross income
## Rating: customer stratification rating on their overall shopping experience (on a scale of 1 to 10)



## Import data
```{r}
sales<-read.csv("supermarket.csv",header = TRUE)
head(sales) #check the data frame
```
##rename data frame
```{r}
library(tidyverse)
library(dplyr)
names(sales)
data<-sales%>%
  rename(Id=Invoice.ID,
         Type=Customer.type,
         Product=Product.line,
         Price=Unit.price,
         Tax=Tax.5.,
         gross_percent=gross.margin.percentage,
         gross_income=gross.income) #rename the column is convenient for next step
```

```{r}
data$Date<-as.Date(data$Date,"%m/%d/%y")  #convert the character of Date to date type
```
```{r}
summary(data)
```
## The attachment below obviously display the relationship between the city and branch. we can see the Branch A only shows in City, Yangon, Branch B in City, Mandalay, and the rest in Naypyitaw.
```{r}
library(ggplot2)
data%>%
  ggplot(aes(Date,Total,color=Branch))+geom_point()+facet_wrap(~City) # Point graph display the relationship of Branch and City
```
## The bar table shows the different payment method in secret cities. In Mandalay, the bar table shows Uniform. and Naypyitaw skewed right, and Yangon seems almost symmetric shapes
```{r}
data%>%
  ggplot(aes(Payment,fill=Branch))+geom_bar()+ggtitle("Payment bar table and Branch in different city")+facet_grid(~City)
```
## The attachment is linear regression between the Gender and type of customers where they spend total with date.
```{r}
data%>%
  ggplot(aes(Date,Total, color=Gender))+geom_point()+geom_smooth()+facet_wrap(~Type)+ggtitle("relationship of customer of type and gender graph table")
```
```{r}
data%>%
  ggplot(aes(Date,Total, color=Product))+geom_point()+geom_smooth()
```
```{r}
ggplot(data=data)+geom_bar(mapping= aes(x=Branch, fill=Product), position="dodge")
```
```{r}
ggplot(data=data)+geom_density(mapping= aes(x=Rating,fill=Branch),alpha=0.3)
```
```{r}
data%>%
  ggplot(aes(Rating,fill=Product))+geom_boxplot(position="dodge")+facet_wrap(~Branch,nrow = 3)
```




```{r}
head(data)
```

## Import sql library
```{r}
library(sqldf)
sqldf("select * 
      from data
      group by Id
      order by Rating desc, Total desc
      limit 10")  # use sql code to arrange the data group by Id, then arrange descending by rating and total limit 10 obs
```
```{r}
sqldf(" select count(*)
      from data
      where Type == 'Member'
      ") # counting 501 obs are Membership in 1000 obs in data frame
```












