---
title: "supermarket sales"
authoer: "Mingwei Wu"
date: "11/24/2020"
output: html_notebook
---
## Data Description
### Id: computer generated sales slip invoice indentification number
### Branch: branch of supercenter (3 branches are avaliable identified by A, B and C)
### City: Location of supercenters
### Type: type of customers, recorded by members for customers using member card and normal for without member card
### Gender: gender type of customer
### Product: general item categorization groups - electronic accessories, fashion accessories, food and beverages, health and beauty, home and lifestyle, sports and travel
### Price: price of each product in dollar
### Quantity: numbers of products purchased by customer
### Tax: 5% tax fee for customer buying
### Total: total price including tax
### Date: date for purchase (record available from Jan 2019 to March 2019)
### Time: purchase time (10am to 8pm)
### Payment: payment used by customer for purchase(3 methods are available - Cash, Credit card and Ewallet)
### COGS: cost of goods sold
### Gross income: gross income
### Rating: customer stratification rating on their overall shopping experience (on a scale of 1 to 10)



## Import data
```{r}
sales<-read.csv("supermarket.csv",header = TRUE)
head(sales) #check the data frame
```
###rename data frame
```{r}
library(tidyverse)
library(dplyr)
names(sales)
data<-sales%>%
  rename(Id=Invoice.ID,
         Type=Customer.type,
         Product=Product.line,
         Price=Unit.price,
         Tax=Tax.5.,
         gross_percent=gross.margin.percentage,
         gross_income=gross.income) #rename the column is convenient for next step
```

```{r}
data$Date<-as.Date(data$Date,"%m/%d/%y")  #convert the character of Date to date type
```
```{r}
summary(data)
```

```{r}
library(ggplot2)
data%>%
  ggplot(aes(Date,Total,color=Branch))+geom_point()+facet_wrap(~City) # Point graph display the relationship of Branch and City
```

```{r}
data%>%
  ggplot(aes(Payment,fill=Branch))+geom_bar()+ggtitle("Payment bar table and Branch in different city")+facet_grid(~City)
```
```{r}
data%>%
  ggplot(aes(Date,Total, color=Gender))+geom_point()+geom_smooth()+facet_wrap(~Type)+ggtitle("relationship of customer of type and gender graph table")
```








